Biden Projected to Win in the 2024 US Presidential Election

### 2024-03-15 paper/paper.qmd
added the results section

```
@fig-support-age
In @fig-support-age, we used the data to find the proportion of the voters categorized by age, who would vote for the
Democratic party. We found a pattern that the group of youngest voters and the group of the senior citizen votes are
more likely to vote for the Democratic Party(Biden).

@@

```
@fig-support-sex
@fig-support-sex shows the proportion of Female voters that would vote for the Democratic Party as compared to the Male
voters. We see a 10% difference in the proportion. Here, we see that Women are 10% more likely to vote

@@

@fig-support-general

@@

In the graph showcasing different regions and their voting for biden, we noticed that
This is similar to the findings in https://www.brookings.edu/articles/forecasting-the-presidential-election-what-can-we-learn-from-the-models/
that address the same prediction for 2024. Our model and the article predict that states that support Trump are
from the middle and Midwest parts of the US, whereas coastal states and the Northeast tend to vote for Biden.
Historically, rural, conservative-leaning towns with strong cultural ties to traditional values and industries like manufacturing and agriculture have defined the middle and Midwest regions of the United States.
These areas frequently support gun rights, minimal government intrusion, and religious liberty—issues that are strongly aligned with the agenda of the Republican Party, which Trump advocated. In contrast, the Northeast and coastline states, which are renowned for their progressive views on culture, urban facilities, and diverse populations, have historically tended toward more liberal policies and social ideals that are more in line with the Democratic Party platform, which Biden advocated.

>>>>

In @fig-support-age, we used the data to find the proportion of the voters categorized by age, who would vote for the
Democratic party. We found a pattern that the group of youngest voters and the group of the senior citizen votes are
more likely to vote for the Democratic Party(Biden).

@@

@fig-support-sex shows the proportion of Female voters that would vote for the Democratic Party as compared to the Male
voters. We see more than 10% difference in the proportion. Here, we see that Women are 10% more likely to vote for Biden.
While only 40% of the men in US would vote for Biden, more than 50% of women would vote for the Democratic Party.

@@

@fig-support-general looks at the division of voters for each party. The sample here is all the individuals who took
the survey and what the proportions are in general population of the United States. We see that more than 50% of the
population would vote for Biden or the Democratic Party and the rest would vote for Trump. This graph clearly shows the
conclusion we can deduce from our research that with this survey done in 2022, it is clear that the population of the
United States is inclined towards the Democratic Party.

@@

In the graph showcasing different regions and their voting for biden, we noticed that
This is similar to the findings in https://www.brookings.edu/articles/forecasting-the-presidential-election-what-can-
we-learn-from-the-models/
that address the same prediction for 2024. Our model and the article predict that states that support Trump are
from the middle and Midwest parts of the US, whereas coastal states and the Northeast tend to vote for Biden.
Historically, rural, conservative-leaning towns with strong cultural ties to traditional values and industries like
manufacturing and agriculture have defined the middle and Midwest regions of the United States.
These areas frequently support gun rights, minimal government intrusion, and religious liberty—issues that are strongly
aligned with the agenda of the Republican Party, which Trump advocated. In contrast, the Northeast and coastline states,
which are renowned for their progressive views on culture, urban facilities, and diverse populations, have historically tended toward more liberal policies and social ideals that are more in line with the Democratic Party platform, which Biden advocated.
